A weakly structured stem for human origins in Africa

### 2022-03-11 paper.tex
A few small changes to the last paragraph

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb}
(see also Section \ref{sec:morpho_diff}).
This correspondence allows predictions of our model to be related to the fossil record.
The fossil record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar to contemporary humans
(e.g., from Omo Kibish, Ethiopia \citep{Day1969-rh,Vidal2022-qe}),
others are similar in some features but not others
(e.g., from Jebel Irhoud, Morocco \citep{Hublin2017-cq,Richter2017-zu}),
and others are very different
(e.g., from Dinaledi, South Africa \citep{Berger2015-bq,Dirks2017-uk}) in morphology.
If, as our model predicts, the
genetic differences between the stems were comparable to those among
contemporary human populations, the most morphologically divergent fossils are unlikely to
represent branches that contributed appreciably to contemporary human
ancestries.

>>>>

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb}
(see also Section \ref{sec:morpho_diff}).
This correspondence allows predictions of our model to be related to the fossil record.
The fossil record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar in morphology to contemporary humans
(e.g., from Omo Kibish, Ethiopia \citep{Day1969-rh,Vidal2022-qe}),
others are similar in some morphological features but not others
(e.g., from Jebel Irhoud, Morocco \citep{Hublin2017-cq,Richter2017-zu}),
and others are very different in morphology
(e.g., from Dinaledi, South Africa \citep{Berger2015-bq,Dirks2017-uk}).
If, as our model predicts, the
genetic differences between the stems were comparable to those among
contemporary human populations, the most morphologically divergent fossils are unlikely to
represent branches that contributed appreciably to contemporary human
ancestries.
